Freezing of a Weeks-Chandler-Anderson Fluid using Classical Density Functional Theory

### 2021-01-13 papers/thesis-kirstie/thesis.tex
edits

A liquid will eventually freeze as heat is removed, or the liquid is compressed, and 
the density will change abruptly at the phase transition.
The particular structure and density that result are affected 
by the interatomic potential. When repulsive, soft sphere fluids 
(that are not too soft) freeze, they form lattice structures composed of 
Face Centered Cubic (FCC) crystal cells~\cite{Hansen}, as do hard spheres. 
This structure is what one would see by filling a box with marbles. It 
results in the highest density achievable for hard, and nearly-hard, spheres 
that are purely repulsive.

>>>>

%A liquid will eventually freeze as heat is removed, or the liquid is compressed, and 
A liquid will freeze when its free energy is lower than the free energy
that a solid would have under the same conditions.
At the phase transition the density will change abruptly, and
the particular structure and density that result will be affected 
by the interatomic potential. When repulsive, soft sphere fluids 
(that are not too soft) freeze, they form lattice structures composed of 
Face Centered Cubic (FCC) crystal cells~\cite{Hansen}, as do hard spheres. 
This structure is what one would see by filling a box with marbles. It 
results in the highest density achievable for hard, and nearly-hard, spheres 
that are purely repulsive.
